Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

As a consequence, many link prediction methods have been proposed with the aim of recovering the missing links. A graph could be associated with external information sources, so called "side information". Therefore, a link prediction method attempts to exploit the graph topology and side information to build a the model for predicting the presence or absence of link any between couple of nodes. An expected method is required to make use of both such kind of data sources. In this paper, we only focus on the topological information. Thus we the term link prediction methods to refer to topology-based link prediction methods. Concerning link prediction methods, we can classify into two classes: unsupervised learning and supervised learning.

Unsupervised learning methods compute the scores for node couples based on topological features and directly use these scores to consider non-observed links to be present or absent. In \cite{adamic}, a method, \textit{Adamic-Adar}, is proposed in which a score between two nodes is computed by a weighted sum over their common nodes. Nodes with smaller degree are weighted more comparing to the higher ones. Another method also considers node degree when computing proximity is presented. The probability of a existing link connecting two nodes is proportional to the product of their node degrees. Different from the method in \cite{adamic} which considers the common nodes, a link prediction method, \textit{Katz}, is introduced in \cite{katz} that takes into account the number of common paths with different lengths between two nodes to measure the proximity between them. The shorter paths are given more weights, meanwhile the longer ones are weighted less. Another method which is a modification of \textit{Katz} notated as Leicht-Holme-Newman is presented in \cite{lhni}. In this method the similarity of a node couple is based on an assumption that two nodes are more similar if they have more similar intermediate nodes. Besides, in \cite{matrix-factorization} they also apply a raw singular value decomposition, SVD, on the adjacency matrix for link prediction. Generally, unsupervised learning methods takes the advantage from their complexity since they do not face with learning process. However, in many case, they do not show impressing results.

@@

>>>>

Unsupervised learning methods are non-adaptive, and hence computationally efficient, and define a score for any node pair that is proportional to the existence likelihood of an edge between the two nodes. \textit{Adamic-Adar} \cite{adamic} computes the weighted sum over the common neighbors where the weight is inversely proportional to the (log of) each neighbor node degree. The \textit{preferential attachment} method computes a score simply as the product of the node degrees in an attempt to exploit the 'rich get richer' property of certain network dynamics. \textit{Katz} \cite{katz} takes into account the number of common paths with different lengths between two nodes, assigning more weight to shorter paths. The \textit{Leicht-Holme-Newman} method \cite{lhni} computes the number of intermediate nodes. In \cite{matrix-factorization} the score is derived from the singular value decomposition of the adjacency matrix.

@@

In this work we present a novel supervised approach based on pure topological information.
